\documentclass[twoside]{article}

\title{SK Story}

\author{SK}

\date{\today}

\usepackage[margin=0.8in]{geometry}

\setlength{\parindent}{0in}

\begin{document}

\pagenumbering{arabic}

\section{One}

Eoin looked through the roughly hewn window of his tutor's circular stone cottage, watching his elder sister, Brienne, ride through the village gates on her jet black stallion. She held her head high under the heavy tangle of auburn braids interwoven with ceremonial feathers and bands. In the dull overcast sky, typical of the fading winter, the red and yellow plumes and the polished oak crossbow slung across her back burned the eyes of onlookers. And many in number they were - the entire lower town swarmed around her, excited to hear the news she had undoubtedly brought back with her. She smiled down at them all, a small, proud smile that seemed to say she deserved every bit of attention they lauded upon her, but never stopped pushing her stead forwards in the direction of the Keep. When the great bells rang, more people seemed to pour out from their huts, the marketplace, the brothels, everywhere, like so many insects catching the scent of something sweet.
The bells were still clanging when a group of armour clad Red Capes appeared, mounted on their great destriers. They gave the warrior's salute and placed themselves around Brienne like a blockade. The people cheered, but, up here on this hill,  it sounded like a mere murmur punctuated by metallic coughs and Eoin felt far away and disconnected from it all. He caught himself wondering  - and doubting - the type of reception he'd receive if he came bounding in on his stead. He glared at the townspeople resentfully; Brienne and the Red Capes cared little for them, but still they were worshipped. Peasants, illiterates, though they were, were they truly so stupid? He flicked a paper ball out of the window, growling quietly; idiots, all of them idiots...
"I told you that if I caught you staring out of that window one more time, I'd flay you and leave you out for the beasts-"Kynthelig had returned, bringing with him a violent thump that racked his chest-"what are you staring at this time, huh? Why'd you think-ah..."
Eoin ignored him and turned back to his rune work, mildly resentful. He knew that if he cared to look up at this moment, he would have been treated to a look on Kynthelig's face that clearly gave away his unrequited feelings, but his body was still reeling from the force of the fresh blow. Pushing three small pebbles into place with two fingers, he glowered and watched unimpressed as each glyph on the smooth stones flashed in quick succession. In the time it took for Kynthelig to finally tear himself away from the window, a number of runes had flashed again, this time their glow fading perceptibly slower. Eoin noted down which symbols had lit up in his notebook.
Mir. Eth. Cal.
He smiled ruefully as he decoded the message, but Kynthelig was not amused. "Ever the little entertainer, isn't he, our Maccus."
Eoin said nothing. Taking his chance while his tutor was distracted, he separated Mir, Dus and Err, lining them up so that they connected in sequence. Just as before, they lit up briefly, but Kynthelig had turned to look before Eoin could spread the runes.
"I saw that," he said sharply, "you could sleep for a hundred years, eh?" Eoin tensed, expecting a rebuke, but his tutor sighed wearily, "well, I suppose it is late enough. It is almost evenfall and I suppose they'll summon me... Go on, get out of it-"and he shooed him out of his cottage.
Eoin knew Kynthelig was only letting him go so that he could get down to the Veil of Wanderers and see his precious Brienne again. He smirked. For all his honour and repute in the eyes of men, Kynthelig was a fool. What was there to like about Brienne? It was a complete mystery to Eoin... But, for now, he didn't care. He was finally free. Without glancing over his shoulder, he ran deeper into the hills Kynthelig's cottage sat upon, running hard and fast in the opposite direction of the towncentre. The great smith of the sky was battering the heavens again, Eoin thought as he looked up at the twilit sky; the metal grey of the clouds was tempered into a blaze of reds and oranges that burned brightly as the golden disc of the sun set. Soon, the stars would appear.
Maccus was quick to catch up with him, meeting him at the usual spot. There was nothing to be said about this spot except that it was very unremarkable and that was why they had chosen it. They were very secretive boys.
"Gods," Maccus exclaimed when he laid eyes on Eoin, "I said class was killing me, not that it was putting me to sleep, though you were right - I'd rather sleep ten years than sit through another rune class with only Kevan to keep me company." He threw himself down and leant against a tree, catching his breath after the run, "your sister's back, did you know?"
"Yeah," Eoin shrugged impassively, "I saw." Who could have missed booming bells?
"Reckon she managed to get hold of the resonator?"
"Dunno." Eoin didn't fancy talking about Brienne much and he knew Maccus knew that, but Maccus was as stupid as Kynthelig in certain aspects.
"Bet she did," Maccus had an impressed smile on his face like it had already happened.
"Well, why don't you go find out then?"
"Alright, alright," Maccus grinned and lithely jumped back onto his feet again, "so, where to?"
Eoin regarded the short, mousey brown haired boy, and stood up slowly. Being of the same age and both of highblood, they had shared almost everything growing up, but where Maccus was light and laughter, Eoin was not, and oftentimes this made him a little resentful; perhaps that was what knowing a mother's love would do for a boy, he thought sullenly.
Eoin turned away and looked out across the fertile valley spreading below them. Out here, just beyond the limits of the lower town, there were fewer guards, fewer spies, no Brienne, no Kynthelig, no Father. Patrols roved around in packs and small watch towers were in place, but nobody cared overmuch about what lay north of the town. They relied on the stopping power of the wide, rushing river that coursed by, swollen by the winter melts, and, not far beyond that, the rocky precipice that fell steeply down.
"The caves," Eoin said at last, "let's go to the caves."
Maccus looked a little apprehensive, "the waters fill them half full at this time of year."
Eoin made a face, "what, you chicken?"
Maccus's pride was hurt, "what? No! Fine - I'll race you there!" And he was off.
Eoin grinned as he followed behind; Maccus was easy to manipulate. He would let him win the race now to restore his pride and Eoin still would have got what he wanted. Feeling little blades of grass brushing his feet between the strips of his leather sandals, he breathed in the cool, clean air, listening to the rush of the river grow louder and louder like the blood pounding in his ears.


\end{document}
